Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-17 surfaces-write-up/surface-write-up.tex

Our first aim in this section is to prove Theorem ~\ref{thm:proj-generators-relations} bounding the number of generators and relations of $R_D$. Before doing so, we justify the assumption ~\eqref{eqn:pm-basis-assumption} through a several convincing examples.

@@

In this section, the main aim is to prove Theorem ~\ref{thm:hirz-generators-relations}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.

>>>>

Our first aim in this section is to prove Theorem ~\ref{thm:proj-generators-relations} bounding the number of generators and relations of $R_D$. Before doing so, we justify the assumption ~\eqref{eqn:bpm-basis-assumption} through a several convincing examples.

@@

In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.
